---
title: "SEMS opgaver"
output:
  html_document:
    df_print: paged
---
##Opgave 7.1

```{r} 
library(Epi)

data71 <- matrix(c(15,1712,41,3188),ncol=2,byrow = TRUE)

twoby2(data71)
```

```{r}

data72 <- matrix(c(581,126,86,776,230,19,17,34),ncol=2)

data72

matrix(apply(data72, 1, sum),nrow = 4)%*%(matrix(apply(data72,2,sum),nrow = 1))/sum(data72)

chisq.test(data72,correct = FALSE)

data72_b <- matrix(c(776,34,26,4),ncol=2,byrow = TRUE)

data72_b

matrix(apply(data72_b, 1, sum),nrow = 2)%*%(matrix(apply(data72_b,2,sum),nrow = 1))/sum(data72_b)

chisq.test(data72_b,correct = FALSE)

Satisfaction <-
  as.table(array(c(1, 2, 0, 0, 3, 3, 1, 2,
                   11, 17, 8, 4, 2, 3, 5, 2,
                   1, 0, 0, 0, 1, 3, 0, 1,
                   2, 5, 7, 9, 1, 1, 3, 6),
                 dim = c(4, 4, 2),
                 dimnames =
                   list(Income =
                          c("<5000", "5000-15000",
                            "15000-25000", ">25000"),
                        "Job Satisfaction" =
                          c("V_D", "L_S", "M_S", "V_S"),
                        Gender = c("Female", "Male"))))

Satisfaction
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
