---
title: "SEMS opgaver"
output:
  html_document:
    df_print: paged
---
##Opgave 7.1

```{r} 
library(Epi)

data71 <- matrix(c(15,1712,41,3188),ncol=2,byrow = TRUE)

twoby2(data71)
```

```{r}

data72 <- matrix(c(581,126,86,776,230,19,17,34),ncol=2)

data72

matrix(apply(data72, 1, sum),nrow = 4)%*%(matrix(apply(data72,2,sum),nrow = 1))/sum(data72)

test72 <- chisq.test(data72,correct = FALSE)

data72_b <- matrix(c(776,34,26,4),ncol=2,byrow = TRUE)

data72_b

matrix(apply(data72_b, 1, sum),nrow = 2)%*%(matrix(apply(data72_b,2,sum),nrow = 1))/sum(data72_b)

chisq.test(data72_b,correct = FALSE)

```

```{r}
data91 <- matrix(c(85,1821,77,2400),ncol = 2,byrow=TRUE)

twoby2(data91)

data91_2 <-
  as.table(array(c(33,48,923,1722,
                   52,29,898,678),
                 dim = c(2,2,2),dimnames=
  list(
    housing=c('rented','owner'),
    CHG=c('yes','no'),
    Smoke=c('Non Smokers','Smokers')
  )))

data91

mantelhaen.test(data91_2)

twoby2(data91_2[,,1])
twoby2(data91_2[,,2])
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
